Chatbots and messaging platforms in the classroom: an analysis from the teacher's perspective

### 2023-01-09 edubots_surveys.Rnw
Update edubots_surveys.Rnw
Co-authored-by: Alberto Guillén <aguillen@ugr.es>

The results, when grouping by teaching experience, confirm that
experienced teachers are just as open to change and willing to embrace new
technological challenges as younger teachers. 
From this concrete plot it is interesting as well to observe the fact that very few
young teachers are willing to use chatbots for other uses. This
reinforces the hypothesis thrown at the beginning of this section that younger
teachers have less experience to consider new ways of using chatbots in their daily work.

>>>>

The results, when grouping by teaching experience, confirm that
experienced teachers are just as open to change and willing to embrace new
technological challenges as younger educators. 
From this concrete plot it is interesting as well to observe the fact that very few
young teachers are willing to use chatbots for other uses. This
reinforces the hypothesis thrown at the beginning of this section that younger
teachers have less experience to consider new ways of using chatbots in their daily work.
